### 2021-02-25 preliminaries.tex
Shorten the paper to 15 pages

Since the space of the derivable clauses is typically very large,
the efficacy of the prover depends on the order in which the inferences are applied.
The common saturation-based \glspl{atp} order the inferences
by maintaining two classes of the inferred clauses: processed and unprocessed \cite{Schulz2019}.
In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
is selected from the unprocessed set
and all the inferences between the given clause and the processed clauses are performed.
The resulting new clauses are added to the unprocessed set.
Finishing the proof in as few iterations of the saturation loop as possible is important
because the number of inferred clauses typically grows exponentially during the proof search.

>>>>

Since the space of the derivable clauses is typically very large,
the efficacy of the prover depends on the order in which the inferences are applied.
The common saturation-based \glspl{atp} order the inferences
by maintaining two classes of the inferred clauses: processed and unprocessed \cite{Schulz2019}.
In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
is selected from the unprocessed set
and all the inferences between the given clause and the processed clauses are performed.
The resulting new clauses are added to the unprocessed set.
Finishing the proof in few iterations of the saturation loop is important
because the number of inferred clauses typically grows exponentially during the proof search.
